Supporting Information

### 2018-03-06 SupportingInformation.Rmd
minor error in fig calling

As described in Methods, each of our statistics, as computed for the 
ranges $0-0.1$, $0.1-0.2$, ..., $0.9-1$, was compared to the distributions 
of values of the same statistic (with the same ranges) on 1000 normal-copula 
surrogate datasets with similar Kendall or Spearman correlations, in different 
runs (`r figure_nums("soilCN_nonparam",display="c")`). Because the correlation 
used in the Cor statistic is the Spearman correlation, Spearman-preserving surrogates
should be used, so the top-left panel of `r figure_nums("soilCN_nonparam",display="c")`
should be ignored (DAN: need to fix this). Results indicate
DAN: continue here.

>>>>

As described in Methods, each of our statistics, as computed for the 
ranges $0-0.1$, $0.1-0.2$, ..., $0.9-1$, was compared to the distributions 
of values of the same statistic (with the same ranges) on 1000 normal-copula 
surrogate datasets with similar Kendall or Spearman correlations, in different 
runs (`r fig_nums("soilCN_nonparam",display="c")`). Because the correlation 
used in the Cor statistic is the Spearman correlation, Spearman-preserving surrogates
should be used, so the top-left panel of `r fig_nums("soilCN_nonparam",display="c")`
should be ignored (DAN: need to fix this). Results indicate
DAN: continue here.
